---
title: "p8105_hw1_zz3039"
author: "Zirui Zhang"
date: "2022-09-21"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Problem 1
```{r chunk_Problem 1, message=FALSE, warning=FALSE}
library(palmerpenguins)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

* The names of the variables in *penguins* are:
*`r names(penguins)`*.

* The levels of each *factor variables* are:

  *species:* `r levels(penguins$species)`;

  *island:* `r levels(penguins$island)`;

  *sex:* `r levels(penguins$sex)`.

* The dataset *penguins* has **`r nrow(penguins)`** rows and **`r ncol(penguins)`** colums.

* The *mean flipper length* of *penguins* is **`r mean(penguins$flipper_length_mm, na.rm = TRUE)`**.

* This is a scatterplot of *flipper length* vs *bill length*:

```{r chunk_ggplot, message=FALSE, warning=FALSE}
P1_plot =
  ggplot(
    penguins, 
    aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(size = 0.5, color = "dark green") + labs(x = "Bill Length", y = "Flipper Length")
P1_plot
ggsave(file = "Scatterplot.png", plot = P1_plot)
```


## Problem 2

### Create a data frame
```{r chunk_Problem 2, message=FALSE, warning=FALSE}
library(tibble)
P2_df =
  tibble(
    a = rnorm(10),
    logical = a > 0,
    b = "Star&Sheep",
    c = factor(c(0, 0.5, 1, 0, 0.5, 1,0, 0.5, 1, 0)))
P2_df
mean(pull(P2_df, a), na.rm = TRUE)
mean(pull(P2_df, logical), na.rm = TRUE)
mean(pull(P2_df, b), na.rm = TRUE)
mean(pull(P2_df, c), na.rm = TRUE)
```

### Convert variables
```{r chunk_P2, eval=FALSE}
as.numeric(pull(P2_df, logical))
as.numeric(pull(P2_df, b))
as.numeric(pull(P2_df, c))
```
* Logical and factor vectors can be converted to numeric vectors while character vectors can not. This helps explain why it works when taking the mean of the logical vectors as they were returned as 0 and 1; for factor vectors, they were returned as their underlying numeric representaions after been converted.

