---
title: "p8105_hw1_zz3039"
author: "Zirui Zhang"
date: "2022-09-21"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Problem 1
```{r chunk_Problem 1, message=FALSE, warning=FALSE}
library(palmerpenguins)
library(tidyverse)
data("penguins", package = "palmerpenguins")
glimpse(penguins)
# the data in this dataset, including values of important variables;the mean flipper length
```

* The names of the variables in "penguins" are:
`r names(penguins)`.

* The dataset "penguins" has `r nrow(penguins)` rows and `r ncol(penguins)` colums.

* The mean flipper lenghth of "penguins" is `r mean(penguins$flipper_length_mm)`.


```{r chunk_ggplot, message=FALSE, warning=FALSE}
P1_plot =
  ggplot(
    penguins, 
    aes(x = bill_length_mm, y = flipper_length_mm))+
  geom_point(size = 0.5, color = "dark green")+
  labs(x = "Bill Length", y = "Flipper Length")
P1_plot
ggsave(file = "Scatterplot.png", plot = P1_plot)
```


## Problem 2

### Create a data frame
```{r chunk_Problem 2, message=FALSE, warning=FALSE}
library(tibble)
P2_df =
  tibble(
    a = rnorm(10),
    logical = a > 0,
    z = "Star&Sheep",
    b = factor(c(0, 0.5, 1, 0, 0.5, 1,0, 0.5, 1, 0)))
P2_df
mean(pull(P2_df, a))
mean(pull(P2_df, logical))
mean(pull(P2_df, z))
mean(pull(P2_df, b))
```

### Convert variables
```{r chunk_P2, eval = FALSE}
as.numeric(pull(P2_df, logical))
as.numeric(pull(P2_df, z))
as.numeric(pull(P2_df, b))
```
Logical and factor vectors can be converted to numeric vectors while character vectors can not. This helps explain that it works when taking the mean of the logical vectors as they were returned as 0 and 1; for factor vectors, they were returned as their underlying numeric representaion after been converted.

